---
title: "Lab 4 Tidy data (50 points)"
author: "Fang Fang"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Delivery:

1.Answer 8 questions in a word document. 

2.You should also submit a .csv file. 

3.You have 10 bonus points at the end of this lab. 



## Steps:

### 1. Import the dataset.
 
```{r eval=FALSE}
library(tidyverse)
air<- read_csv("data/air_raw_upload.csv")
```


### Question 1: (5 points)
How many rows and columns does this dataset have?

Answer:  1440 rows and 17 columns

### Question 2: (5 points)
Is this dataset tidy or messy? Why?

Answer: Messy. The station and variables are mixed up, and the column names are not a certain attribute, they are certain values. 

                
### Question 3:(5 points)
How many rows and columns does air_v1 have? 
```{r eval=FALSE}
air_v1 <- pivot_longer(air,cols=(-c("Date","Time")),
        names_to="mix",values_to="measured_value")
```




### Question 4:(5 points)
Examine air_v2. Why is this dataset a messy data? 
```{r eval=F}
air_v2 <- separate(air_v1, sep=" ",mix, c("Station","Meteorological variable"))
```

Answer: Yes it is still messy. The meteorological variables should have their own columns. 

### Question 5: (10 points)
Based on your answer above, select one of the following functins `separate`, `unite`, `pivot_longer` to make air_v2 clean. Name the output as air_v3. 
```{r eval=F}
air_v3 <- pivot_wider(air_v2,names_from="Meteorological variable",  
    values_from="measured_value")
```

### Question 6: (5 points)
After you execute the function you choose above, How many rows and columns do you have for this clean dataset (air_v3)? 

Answer: 4320 rows and 8 columns. 





### Question 7:(10 points)

Among the three stations, which one has the highest average temperature? 

Hint: Once your dataset is clean, let's use tapply to calculate the average by 3 stations. You need to exclude the NAs. 

Note you need to provide both your `tapply` code and answers for question 7. 
```{r eval=F}
tapply(air_v3$TEMP,air_v3$Station,mean, na.rm=T)
```

Answer: BERESFIELD: 24.22

### 4. Export and submit your assignment. 


Make sure you have a subfolder called "output". Then execute the code below.


```{r eval=FALSE}
write_csv(air_v3,"output/Fang_lab4.csv")
```



### Question 8:(5 points)
Submit this .csv file. 



# This is the end of Lab 4. 

### Bonus: (10 points)

1) Examine the output called air_v3. Does it still contain NAs? (5 points)
Answer: Yes it contains NAs since some stations do not have all the measurements

2) Try to use `drop_na` function to exclude all the NAs in air_v3. Name the output air_v4. Export air_v4 as a csv and turn it in compass (5 points).    

Hint: you can use `?drop_na` to know more about this function. 

```{r eval=F}
air_v4 <- drop_na(air_v3)
write_csv(air_v4,"output/air_v4.csv")
```

Answer: the drop_na function will exclude entire row if any NA appears
